A Recipe for Scavenging \textcolor{blue}{in Vertebrates} - the natural history of a behaviour

### 2016-08-09 response_letter.tex

\begin{enumerate}
\item{Abstract: Scavenging can be difficult to observe, but probably no more so than predation.
Also, using experimental carcasses, scavenging is actually quite easy to observe.}

\textcolor{blue}{We emphasise that food webs have tended to lump all carnivory into predation and it is with extinct species that we have no observational evidence.}

\item{Abstract: You should point out that your ``scale of scavenging'' is only qualitative; you made no attempt to quantify such traits.}

\textcolor{blue}{We now emphasise that our scale is qualitative here and throughout the manuscript.}

@@

\item{Introduction: Much of this section seems to follow DeVault's (2003) review paper on scavenging—in fact, there is almost nothing new here that is not covered in that earlier review.}

\textcolor{blue}{We have rewritten the introduction to more accurately reflect the aim of this review i.e. that the scavenging gradient allows us to infer scavenging in the fossil record as well as in modern species. In making this revision we have reduced overlap with De Vault (2003) considerably.} %TG:

@@

\item{Introduction: You mention that you will use ``other methods in order to discern the most suitable morphologies...''  but you don't say what they are. What other methods are you talking about?}

\textcolor{blue}{We now specify the approaches we have in mind:  \textit{``e.g. energetics models, comparative anatomy, palaeontology etc.'' }}

\item{I think that early on in the paper you need to define obligate and facultative scavengers and then throughout the paper, specify which you are referring to. For example, in the first sentence of the Detection section, you talk about ``known scavengers'', but it is unclear if you really mean obligate scavengers. Nearly all carnivorous vertebrates are scavengers at least to some extent, so you need to elaborate on what you mean when you talk about ``scavengers''.}

\textcolor{blue} {We make the following point in our introduction: \textit{``Indeed, there is no discrete divide between predators and scavengers but rather a continuous gradient. Even vultures, the canonical example of obligate scavengers, can hunt.''} We have tried to be clearer throughout the paper as well by removing references to this division.}

@@

\item{Page 6, 12: In your discussion of aquatic scavengers, you might want to refer to Beasley et al. (2012; Oikos 121:1021-1026).}

\textcolor{blue}{We have included this reference and explicitly discuss how differences in the physical properties of water Vs air can affect scavenging: \textit{``The physical differences between water and air mean carcass availability is radically different between these environments (Beasley et al. 2012). For one, carcasses get moved around by water which results in a more diffuse signal being produced for would-be scavengers. Carcasses also tend to sink in water where they are no longer accessible to pelagic scavengers (Beasley et al. 2012). Research has shown that an animal need only travel between 16 to 36 km to encounter a fresh whale carcass  (Mole\'{o}n and Sánchez-Zapata 2015). The phenomenon of occasional bounties of carrion in the form of these whale falls has led some researchers to investigate if an obligate scavenger could survive by seeking out these remains exclusively.''}}

\item{Page 6: Why is jaw morphology likely to define scavengers?  Please elaborate.}

\textcolor{blue}{We now avoid discussion of jaw morphology at this early point in the manuscript, and later develop fully our ideas on how feeding anatomy can be related to propensity to exploit scavenging opportunities.}
%TG: Note that there's no change in the text here. Just a lecture on jaw morphologies. We might want to elaborate a bit in the manuscript.

@@

% All of the examples we use are backed up by references from previous work.
% But this is hardly unique to our work.

\bigskip

While the authors distinguish between obligate and facultative scavenging, they tend to lump them together when it comes to constructing their arguments.
In the end, is the argument about the former, or the latter? Is the real interest in whether species scavenge at all, what proportion of their resources are obtained by scavenging, or what the conditions are that produce facultative or obligate scavengers?

\textcolor{blue} {This was also raised by reviewer 1.
We make the following point in our introduction: \textit{``Indeed, there is no discrete divide between predators and scavengers but rather a continuous gradient. Even vultures, the canonical example of obligate scavengers, can hunt.} We have tried to be clearer throughout the paper as well. Indeed, this is a key point of our review paper: to change our view of scavenging from the classic dichotomy of obligate and facultative scavengers, to a sliding scale depending on the species and the ecosystem.''}

They also seem to ignore flexibility in species' behaviors.
For instance, while spotted hyenas are on their highly scavenging side of their Figures 1 and 2, in some ecosystems they hunt significant proportion of their prey.
Similarly, lions can take a large proportion of their prey as scavenged, as the authors note.
But to suggest, as they do in their abstract, that they can apply their scale of scavenging to any species at any time to judge how important scavenging was in its diet is frankly completely ignoring behavioral variability over time and space. 
\bigskip

\textcolor{blue}{It is undoubtedly true that scavengers can be variable in the proportion of carrion they consume but we would argue that species like hyenas have certain characteristics that make this possible.
In contrast, cheetahs do not have a biology that lends itself to scavenging in the wild, due to poor competitive ability etc.
We appreciate that there is a continuum across and among species which we specifically note in this revised version. 
As we note in the above comment, a combination of a species' traits, and the state of the ecosystem they find themselves in will determine their scale of scavenging. 
Search rates can be altered by environmmetal or ecological conditions as well as intrinsic traits of the forager. 
So, far from invalidating our idea it reinforces it.
Moreover, researchers working in palaeobiology often try to reconstruct the behaviours of extinct species; we are following this approach when we make inferences about ancient systems.}
\bigskip

It is substantially more difficult with fossil species for which we may know far fewer of the variables they list in Figure 1, in a nuanced way.
Figure 2 does not display the diversity of scavengers through time, it displays examples of species that display observed or inferred scavenging behaviors.
Diversity has specific ecological definition(s) that are being ignored here.
\bigskip

@@

\textcolor{blue}{It is undoubtedly true that scavengers can be variable in the proportion of carrion they consume but we would argue that species like hyenas have certain characteristics that make this possible.
In contrast, cheetahs do not have a biology that lends itself to scavenging in the wild, due to poor competitive ability etc.
We appreciate that there is a continuum across and among species which we specifically note in this revised version. 
As we note in the above comment, a combination of a species' traits, and the state of the ecosystem they find themselves in will determine their scale of scavenging. 
Search rates can be altered by environmmetal or ecological conditions as well as intrinsic traits of the forager. 
So, far from invalidating our idea it reinforces it.
Moreover, researchers working in palaeobiology often try to reconstruct the behaviours of extinct species; we are following this approach when we make inferences about ancient systems.}
\bigskip

It is substantially more difficult with fossil species for which we may know far fewer of the variables they list in Figure 1, in a nuanced way.
Figure 2 does not display the diversity of scavengers through time, it displays examples of species that display observed or inferred scavenging behaviors.
Diversity has specific ecological definition(s) that are being ignored here.
\bigskip

\textcolor{blue}{Figure 2 has been removed and figure 1 has been expanded.}

%TG: They make a point here (although their diversity definition rant is completely out of topic). Should we just drop figure 2 and use it as an abstract/press release picture? AK Agreed 
\bigskip

If the authors chose to resubmit, I would suggest they organize their manuscript based on known information about modern species, known (e.g. bone processing by theropods) and inferred (e.g. scavenging in hominins) information about fossil species, and then try to draw broader conclusions.
They might look to articles about other modern scavenging opportunities such as Capaldo and Peter's study of wildebeest drownings \url{http://www.sciencedirect.com/science/article/pii/S0305440385700398}, and suggestions that sabertooth cats which they claim were unable to feed on bones may have consumed more bone than penecontemporaneous dire wolves \url{https://www.jstor.org/stable/20627167?seq=1#page_scan_tab_contents}.

\textcolor{blue}{The issue of the structure of our paper was noted by all reviewers who all had suggestions to improve it. 
We have made an effort to delineate all of the main sections and subsections so that our frame of optimal foraging is more apparent.
We have added the two suggested references to our paper.}

\bigskip
In sum, while I think the aim of the article is a very worthwhile one, I think the authors cannot claim to have produced an all-encompassing model that can predict the presence or level of scavenging in any organism - because I think this simply cannot be done.

@@

\section{Reviewer: 3}
This is a well-written, enjoyable manuscript that assesses the functional traits associated to past and, mostly, current major vertebrate scavengers.
As a result, the authors provide a sort of guide to identify the extent of scavenging behaviour among carnivores in both current and past ecosystems.
I have several suggestions that should be considered before publication (please see below).

\subsection{Major comments:}

\begin{enumerate}
\item{Invertebrates are ignored completely throughout the ms.
Please specify in the Introduction that this review focuses on vertebrate scavengers.
In this line, I recommend to include ``in vertebrates'' at the end of the title to be more specific.
Also, in the ``Competition'' section you mention competition with vertebrates and micro-organisms, but not with invertebrates.
You should consider them in this section (and in ``Facilitation''; see next point).}

\textcolor{blue}{We changed the title of the manuscript to ``A Recipe for Scavenging in Vertebrates - the natural history of a behaviour''. We have added two mentions of inverebrates as competitors to the manuscript but given our focus these are not expanded upon.}
%TG: Also maybe mention invertebrates in the competition part of the manuscript. + For a response to the reviewer, here is probably a good point for stating clearly that we wanted this manuscript to be focusing more on vertebrates because of the palaeo aspect. Both micro-organisms and invertebrates (I guess mainly arthropods) are unlikely to display preserved morphological clues for suggesting a scavenging behaviour because of their poor preservation anyway.

@@

\item{I found difficult to follow the main point of the paper because the ms is not well organized. Following a hierarchical order, I'd define four/five main sections: ``Introduction'', ``The Challenges of Scavenging'' (this could be a subsection within the previous section), ``Encounter Rate'' (with four different subsections: ``Metabolism'', ``Locomotion'', ``Sensory Detection'' and ``Carcass Availability''), ``Handling Time'' (which would include ``Food Processing'') and ``Conclusion''. \\

Moreover, ``Competition'' and ``Facilitation'' (I strongly encourage you to consider not only competitive, but also facilitative processes, which are mostly neglected in your review) should be treated as transversal factors that can modulate each of the abovementioned parameters. Thus, I'd include them in a different section, or mention the competitive and facilitative processes related to each parameter within each subsection. Fig. 1 should be re-organized accordingly.}

\textcolor{blue}{We clarified the structure of the manuscript by introducing clearer hierarchical subsections, an additional section on facilitation and a revised figure 1.}
%TG: + more blabalal on his ``Facilitation'' part

@@

\item{The use of the scientific literature on scavenging is deficient, especially for a review paper like this. A number of key references are missing, e.g., Selva \& Fortuna (2007 Proc. R Soc. B 274:1101-1108), Wilson \& Wolkovich (2011 TREE 23:129-135), Beasley et al. (2012 Oikos 121:1021-1026), Cort\'{e}s-Avizanda et al. (2012 Ecology 93:2570-2579), Cort\'{e}s-Avizanda et al. (2014 Ecology 95:1799-1808), Mole\'{o}n et al. (2014 Biol. Rev. 89:1042-1054), Pereira et al. (2014 Mammal Rev. 44:44-55), P\'{e}riquet et al. (2015 Biol. Rev. 90:1197-1214), Mateo-Tom\'{a}s et al. (2015 Divers. Distrib. 21:913-924), Mole\'{o}n \& S\'{a}nchez-Zapata (2015 BioScience 65:1003-1010), Moreno-Opo et al. (2016 Behav. Ecol.), Sebasti\'{a}n-Gonz\'{a}lez et al. (2016 Ecology 97:95-105). Your literature synthesis might benefit from the reading of these articles, for instance regarding competitive and facilitative interactions among scavengers. Also, the review would be more informative and useful for readers. Next I mention some particular comments regarding the use of the references (I mention others in Minor comments):}\\

\textcolor{blue}{Thanks very much for these very useful references, all of which are now included and used to bolster some sections of the paper, particularly with respect to facilitation, see below for further details.}

@@

Page 2, 1st sentence: but see Mole\'{o}n \& S\'{a}nchez-Zapata (2015); many of the most charismatic vertebrates of the world are scavengers. Rather than ``scavengers'', what is not charismatic is probably ``scavenging''.

\textcolor{blue}{Our introduction has been rewritten and this passage no longer appears.}

@@

\item{ABSTRACT:} You could remove ``, the first to our knowledge''.

\textcolor{blue}{This has been removed.}

\item{ABSTRACT:} Also, you could mention some relevant specific findings of your synthesis.

\textcolor{blue}{We cannot provide details of specific predictions in sufficient detail to be intelligible within the work limit of the abstract, but have modified the structure of the manuscript to make these stand out more clearly.}

### 2016-08-09 natural history of scavenging.tex
Graeme's comments addressed

\begin{abstract} 
Despite its prevalence, scavenging is a difficult behaviour to observe in modern day carnivores and impossible to study directly in extinct species. 
Yet, there are certain intrinsic and environmental features of a species that push it towards a scavenging lifestyle. 
These can be thought of as some of the principal parameters in optimal foraging theory namely, encounter rate, handling time and prey availability. 
We use these components to highlight the morphologies and environments that would have been conducive to scavenging over geological time by focusing on the dominant vertebrate groups of the land, sea and air. 
The result is a synthesis on the natural history of scavenging. 
These features that make up our \textcolor{blue}{qualitative} scale of scavenging can be applied to any given species and allow us to judge the likely importance of this foraging behaviour. 
\textcolor{blue}{Our approach offers, among others, an explanation as to why extinct pterosaurs likely scavenged and why extant bats don't.}    
\end{abstract}

@@

\textcolor{blue}{Historically, food webs have classified most acts of carnivory as predation events \citep{wilson2011scavenging}. 
This is clearly a mistaken view because of the existence of scavenging, a behaviour displayed by almost all carnivorous vertebrates \citep{devault2003scavenging}. 
Recent research has begun to redress this imbalance by recognising the prevalence of scavenging and its implications for trophic ecology across modern ecosystems \citep{pereira2014facultative,periquet2015lion}.
By increasing multichannel feeding and the number of food web links scavenging can give stability to an ecosystem \citep{moleon2015living}. 
Indeed, there is no discrete divide between predators and scavengers but rather a continuous gradient in terms of the proportion of carrion in the diet \citep{pereira2014facultative}.
Even vultures, the canonical example of obligate scavengers, can hunt \citep{margalida2011scavenger}. While it is relatively easy to determine whether a species engages in scavenging through observation, determining the proportion of carrion in the diet requires extensive behavioral data. % (I put this in to placate the reviewer who said it was easy).
Unfortunately, the lack of direct behavioural data makes it even more difficult to discern scavenging from predation among extinct forms where it was surely exhibited by prehistoric vertebrate carnivores.
Some simple heuristics can inform us whether or not the prey was scavenged, for instance, in cases where it was simply too large to have been killed by the ostensible predator \citep{pobiner2008paleoecological}.}
But clearly, a scavenger does not only feed on animals too big for it to have hunted.

@@

\textcolor{blue}{Species that rely on scavenging to sustain substantial portions of their diets must encounter a sufficient amount of carrion in order to meet their energetic demands.
Once found, the scavenger must be able to out-compete any potential competitors and efficiently process the, typically decaying, carcass replete with micro-organism derived toxins \citep{ruxton2014fruit}.}
These characteristics can be assumed to be under evolutionary selection pressures for traits that increase carrion discovery and monopoly.
Finally, the potential for scavenging, in either a species as a whole, or for individuals within a population, will also depend on the density, size, and quality of carcases produced, all of which are affected by complex ecosystem dynamics \textcolor{blue}{\citep{moleon2014inter}. 
Even these aspects can be indirectly impacted by the behaviour of the scavenger \citep{moleon2014inter}.}
Each of these facets are essentially the backbone of fundamental ecological theory and are the key parameters defined in functional response curves, namely encounter rate, handling time and prey availability \citep{jeschke2002predator}.  
By considering scavenging in this context of optimal foraging we can identify the prerequisite attributes and processes required for the behaviour. 
This has enabled us to propose a scale of scavenging whereupon we can place \textcolor{blue}{a given carnivore vertebrate} and assess the likely importance of carrion in its diet.
\textcolor{blue}{We argue that such a scale could be valuable when behaviour can not be observed directly, e.g. for extinct vertebrates.}

@@

\textcolor{blue}{While it is difficult to infer the metabolisms of extinct species, similarities can still also be drawn. Many ectothermic groups such as sharks and bony fish were likely to benefit from the ability to bridge long time-spans between meals such as seen in snakes. In contrast, forms such as dinosaurs \citep{grady2014evidence}, pterosuars \citep{wellnhofer1991illustrated}, some marine reptiles \citep{bernard2010regulation} and some early mammals \citep{lovegrove2016phenology} have been proposed to have possessed at least partial endothermy potentially requiring a higher intake of material in comparison to their ectothermic equivalents. However, such higher metabolic rates would also increased the ability of such species to actively search for carrion.}
%KH: I put this section in as there is no reference in how we can use the above paragraph to infer scavenging in extinct species

@@

While soaring is perhaps the only viable means of locomotion that allows for scavenger to rely entirely on carrion \citep{ruxton2004obligate}, powered flight is still an efficient means of locomotion. 
Certainly, avian flight is cheaper than either walking or running \citep{tucker1975energetic}.

@@

Of course, terrestrial animals can also move bipedally. 
Although the evolution of bipedal movement was significant in that it freed up the forelimbs for other purposes (e.g. climbing, tool-use, wing development etc.) it does not differ radically in cost from quadrupedal locomotion (\cite{williams1999evolution}, \textcolor{blue}{and references therein}). 
For instance, \cite{alexander2004bipedal} shows that, in the case of humans, we are more economical than predicted while walking and less so while running according to predicted costs of terrestrial movement calculated by allometric scaling relationships.
Our locomotory efficiency has fed into the question of where our ancestors placed on the hunter-scavenger axis during the Plio-Pleistocene, which has been a matter of debate for years \citep{dominguez2002hunting}.
\cite{ruxton2013endurance} added to this debate with their argument that long distance endurance running \textcolor{blue}{was not an important feature of hominin scavenging but was instead used by humans for hunting prey by chasing them to exhaustion over large distances.
Even when considering the use of weapons and social foraging, the authors argue that the high cost of running long distances would render it an unattractive foraging strategy for scavenging.}

@@

In addition to fending off other vertebrates, scavengers also have to contend with competition from micro-organisms, which requires a specialised physiology. 
Although the findings of \cite{shivik2006vultures} that ``evolutionary pressures favor detection maximizers relative to toxification minimizers in competitive interactions for carcasses." appear sound, the fact remains that overcoming micro-organism toxins is still a beneficial adaptation to any scavenger. 
Avian scavengers have evolved incredibly acidic stomachs that allow them to consume and process putrefied flesh with no ill effects \citep{houston1975digestive,roggenbuck2014microbiome}. 
This adaptation is not restricted to vultures though, \cite{gremillet2012vultures} showed wandering albatrosses (\textit{Diomedea exulans}; so-called ``vultures of the seas'') had an average pH of 1.5, which enables them to consume fisheries discards and squid carcasses. 
There is also evidence of selection for ``toxification minimizers'' beyond birds among the ectotherms.
From our earlier arguments we know that ecthotherms are limited in their ability to find carrion as quickly as endotherms. 
These later arrivers would thus benefit especially from well-developed detoxifying apparatus. 
\cite{shivik2006vultures} suggests that ``specialized oral structures in snakes may have evolved under pressures associated with scavenging."
Moreover, some researchers have charted an evolutionary course from basal fossorial snakes to modern terrestrial species by way of a scavenging intermediate \citep{bauchot2006snakes}. However, snake venom is primary associated with predation in extant species suggesting that if venom played such a role in extinct species it is no longer its main function \citep{casewell2013complex}.
\textcolor{blue}{In water, by contrast, competition with micro-organisms is significantly reduced because of the high pressures and low temperatures \citep{beasley2012carrion}.}

@@

In Mesozoic systems some large theropod dinosaurs had a morphology indicative of an ability to process bone \citep[e.g. the robust skull and dentition of \textit{Tyrannosaurus rex;}][]{hone2010feeding}.
There is direct evidence that \textit{T. rex} did this in the form of distinctive wear marks on its tooth apices \citep{farlow1994wear,schubert2005wear} and the presence of bone fragments in its coprolites \citep{chin1998king}.
The animal also had an enormous bite force, with one estimate putting it at 57000 Newtons \citep{bates2012estimating} which would have been powerful enough to break open skeletons \citep{rayfield2001cranial}.
Osteophagy may have been even more viable during the Mesozoic era as well because of this skewed body mass distribution of herbivores towards larger sizes \citep{10.1371/journal.pone.0051925}.
When we couple this with the fact that skeletal mass scales greater than linearly with body mass \citep{prange1979scaling} there would have been a lot of bone material to consume in the environment provided an animal had the biology to process it \citep{chure1997one}.

@@

On the ground, and despite the advantages of social resource defence, the competitive ability of even the largest flying bird is radically diminished in their interactions with mammalian competitors, and as such they tend to consume carrion rapidly. 
\cite{houston1974role} observed a group of \textit{Gyps} vultures consuming all of the soft tissue from a 50 kg Grant’s gazelle (\textit{Nanger granti}) in eight minutes. 
Their serrated tongues and hooked bills enable them to achieve this feat \citep{houston1975digestive}. 
Aside from raptors, the specialised beaks of many modern bird lineages tends to hinder their ability to eat meat which is in contrast to the first lineages that did not have this feature \citep{martyniuk2012field}. 
As \cite{martyniuk2012field} notes, \textcolor{blue}{this skull morphology of early birds indicates} they were predominantly carnivorous, implying scavenging was a live opportunity cf. their descendants. 
Among the pterosaurs, \cite{witton2013pterosaurs} makes the case that the istiodactyl pterosaurs were the most likely scavengers of this group based on their potential handling time. 
Their skull morphologies are indicative of animals that were suited to removing large amounts of flesh from an immobile foodstuff \citep{witton2013pterosaurs}.

@@

\section*{Conclusion}
As is often the case in science, the present provides the key to the past.
The animals of today, while often different (sometimes radically so) to their ancestors, can be used to make informed comparisons to extinct species. 
We have used this \textcolor{blue}{approach} to give insight into the drivers of scavenging across vertebrates through time.
In common with any other forager be they grazer, browser or predator, scavengers past and present have had to balance their energetic costs with the gains of food. 
The main factors we considered namely, encounter rate, handling time and prey availability can be used to create a scale of scavenging whereupon any species can be placed in order to establish the importance of carrion in it diet.
We hope this approach will be useful in the effort to explore this most understudied of feeding ecologies.

@@

\section*{Acknowledgments}
Thanks to Natalie Cooper for highlighting the potential for this review, and to Ara Monadjem and Deirdre McClean for their comments on the manuscript.

>>>>

\begin{abstract} 
Despite its prevalence, scavenging is a difficult behaviour to observe in modern day carnivores and impossible to study directly in extinct species. 
Yet, there are certain intrinsic and environmental features of a species that push it towards a scavenging lifestyle. 
These can be thought of as some of the principal parameters in optimal foraging theory namely, encounter rate, handling time and prey availability. 
We use these components to highlight the morphologies and environments that would have been conducive to scavenging over geological time by focusing on the dominant vertebrate groups of the land, sea and air. 
The result is a synthesis on the natural history of scavenging. 
These features that make up our \textcolor{blue}{qualitative} scale of scavenging can be applied to any given species and allow us to judge the likely importance of this foraging behaviour.   
\end{abstract}

@@

\textcolor{blue}{Historically, food webs have classified most acts of carnivory as predation events \citep{wilson2011scavenging}. 
This is clearly a mistaken view because of the existence of scavenging, a behaviour displayed by almost all carnivorous vertebrates \citep{devault2003scavenging}. 
Recent research has begun to redress this imbalance by recognising the prevalence of scavenging and its implications for trophic ecology across modern ecosystems \citep{pereira2014facultative,periquet2015lion}.
By increasing multichannel feeding and the number of food web links, scavenging can confer stability to an ecosystem \citep{moleon2015living}. 
Indeed, there is no discrete divide between predators and scavengers but rather a continuous gradient in terms of the proportion of carrion in the diet \citep{pereira2014facultative}.
Even vultures, the canonical example of obligate scavengers, can hunt \citep{margalida2011scavenger}. While it is relatively easy to determine whether a species engages in scavenging through observation, determining the proportion of carrion in the diet requires extensive behavioral data. % (I put this in to placate the reviewer who said it was easy).
Unfortunately, the lack of direct behavioural data makes it even more difficult to discern scavenging from predation among extinct forms where it was surely exhibited by prehistoric vertebrate carnivores.
Some simple heuristics can inform us whether or not the prey was scavenged, for instance, in cases where it was simply too large to have been killed by the ostensible predator \citep{pobiner2008paleoecological}.}
But clearly, a scavenger does not only feed on dead animals too big for it to have hunted.

@@

\textcolor{blue}{Species that rely on scavenging to sustain substantial portions of their diets must encounter a sufficient amount of carrion in order to meet their energetic demands.
Once found, the scavenger must be able to out-compete any potential competitors and efficiently process the, typically decaying, carcass replete with textcolor{blue}{invertebrates} and micro-organism derived toxins \citep{ruxton2014fruit}.}
These characteristics can be assumed to be under evolutionary selection pressures for traits that increase carrion discovery and monopoly.
Finally, the potential for scavenging, in either a species as a whole, or for individuals within a population, will also depend on the density, size, and quality of carcases produced, all of which are affected by complex ecosystem dynamics \textcolor{blue}{\citep{moleon2014inter}. 
Even these aspects can be indirectly impacted by the behaviour of the scavenger \citep{moleon2014inter}.}
Each of these facets are essentially the backbone of fundamental ecological theory and are the key parameters defined in functional response curves, namely encounter rate, handling time and prey availability \citep{jeschke2002predator}.  
By considering scavenging in this context of optimal foraging we can identify the prerequisite attributes and processes required for the behaviour. 
This has enabled us to propose a \textcolor{blue}{qualitative} scale of scavenging whereupon we can place \textcolor{blue}{a given carnivore vertebrate} and assess the likely importance of carrion in its diet.
\textcolor{blue}{We argue that such a scale could be valuable when behaviour can not be observed directly, e.g. for extinct vertebrates.}

@@

\textcolor{blue}{While it is difficult to infer the metabolisms of extinct species, similarities can still also be drawn. Many ectothermic groups such as sharks and bony fish were likely to benefit from the ability to bridge long time-spans between meals such as seen in snakes. In contrast, forms such as dinosaurs \citep{grady2014evidence}, pterosuars \citep{wellnhofer1991illustrated}, some marine reptiles \citep{bernard2010regulation} and some early mammals \citep{lovegrove2016phenology} have been proposed to have possessed at least partial endothermy potentially requiring a higher intake of material in comparison to their ectothermic equivalents. However, such higher metabolic rates would also have increased the ability of such species to actively search for carrion.}
%KH: I put this section in as there is no reference in how we can use the above paragraph to infer scavenging in extinct species

@@

While soaring is perhaps the only viable means of locomotion that allows for scavenger to rely entirely on carrion \citep{ruxton2004obligate}, powered flight is still an efficient means of locomotion. 
Certainly, avian flight is cheaper per unit distance than either walking or running \citep{tucker1975energetic}.

@@

Of course, terrestrial animals can also move bipedally. 
Although the evolution of bipedal movement was significant in that it freed up the forelimbs for other purposes (e.g. climbing, tool-use, wing development etc.) it does not differ radically in cost from quadrupedal locomotion (\cite{williams1999evolution}, \textcolor{blue}{and references therein}). 
For instance, \cite{alexander2004bipedal} shows that, in the case of humans, we are more economical than predicted while walking and less so while running according to predicted costs of terrestrial movement calculated by allometric scaling relationships.
Our locomotory efficiency has fed into the question of where our ancestors placed on the hunter-scavenger axis during the Plio-Pleistocene, which has been a matter of debate for years \citep{capaldo1995skeletal,dominguez2002hunting}.
\cite{ruxton2013endurance} added to this debate with their argument that long distance endurance running \textcolor{blue}{was not an important feature of hominin scavenging but was instead used by humans for hunting prey by chasing them to exhaustion over large distances.
Even when considering the use of weapons and social foraging, the authors argue that the high cost of running long distances would render it an unattractive foraging strategy for scavenging.}

@@

In addition to fending off other vertebrates, scavengers also have to contend with competition from \textcolor{blue}{invertebrates and micro-organisms, the latter of which may require a specialised physiology.} 
Although the findings of \cite{shivik2006vultures} that ``evolutionary pressures favor detection maximizers relative to toxification minimizers in competitive interactions for carcasses." appear sound, the fact remains that overcoming micro-organism toxins is still a beneficial adaptation to any scavenger. 
Avian scavengers have evolved incredibly acidic stomachs that allow them to consume and process putrefied flesh with no ill effects \citep{houston1975digestive,roggenbuck2014microbiome}. 
This adaptation is not restricted to vultures though, \cite{gremillet2012vultures} showed wandering albatrosses (\textit{Diomedea exulans}; so-called ``vultures of the seas'') had an average stomach pH of 1.5, which enables them to consume fisheries discards and squid carcasses. 
There is also evidence of selection for ``toxification minimizers'' beyond birds among the ectotherms.
From our earlier arguments we know that ecthotherms are limited in their ability to find carrion as quickly as endotherms. 
These later arrivers would thus benefit especially from well-developed detoxifying apparatus. 
\cite{shivik2006vultures} suggests that ``specialized oral structures in snakes may have evolved under pressures associated with scavenging."
Moreover, some researchers have charted an evolutionary course from basal fossorial snakes to modern terrestrial species by way of a scavenging intermediate \citep{bauchot2006snakes}. However, snake venom is primary associated with predation in extant species suggesting that if venom played such a role aiding digestion of discovered carcasses in extinct species it is no longer its main function \citep{casewell2013complex}.
\textcolor{blue}{In water, by contrast, competition with micro-organisms is significantly reduced because of the high pressures and low temperatures \citep{beasley2012carrion}.}

@@

In Mesozoic systems some large theropod dinosaurs had a morphology indicative of an ability to process bone \citep[e.g. the robust skull and dentition of \textit{Tyrannosaurus rex;}][]{hone2010feeding}.
There is direct evidence that \textit{T. rex} did this in the form of distinctive wear marks on its tooth apices \citep{farlow1994wear,schubert2005wear} and the presence of bone fragments in its coprolites \citep{chin1998king}.
The animal also had an enormous bite force, with one estimate putting it at 57000 Newtons \citep{bates2012estimating} which would have been powerful enough to break open skeletons \citep{rayfield2001cranial}.
Osteophagy may have been even more viable during the Mesozoic era as well because of the skewed body mass distribution of herbivores towards larger sizes \citep{10.1371/journal.pone.0051925}.
When we couple this with the fact that skeletal mass scales greater than linearly with body mass \citep{prange1979scaling} there would have been a lot of bone material to consume in the environment provided an animal had the biology to process it \citep{chure1997one}.

@@

On the ground, and despite the advantages of social resource defence, the competitive ability of even the largest flying bird is radically diminished in their interactions with mammalian competitors, and as such they tend to consume carrion rapidly. 
\cite{houston1974role} observed a group of \textit{Gyps} vultures consuming all of the soft tissue from a 50 kg Grant’s gazelle (\textit{Nanger granti}) in eight minutes. 
Their serrated tongues and hooked bills enable them to achieve this feat \citep{houston1975digestive}. 
Aside from raptors, the specialised beaks of many modern bird lineages tends to hinder their ability to eat meat which is in contrast to the first lineages that did not have this feature \citep{martyniuk2012field}. 
As \cite{martyniuk2012field} notes, \textcolor{blue}{this skull morphology of early birds indicates} they were predominantly carnivorous, implying scavenging was a live opportunity compared to many of their descendants. 
Among the pterosaurs, \cite{witton2013pterosaurs} makes the case that the istiodactyl pterosaurs were the most likely scavengers of this group based on their potential handling time. 
Their skull morphologies are indicative of animals that were suited to removing large amounts of flesh from an immobile foodstuff \citep{witton2013pterosaurs}.

@@

\section*{Conclusion}
As is often the case in science, the present provides the key to the past.
The animals of today, while often different (sometimes radically so) to their ancestors, can be used to make informed comparisons to extinct species. 
We have used this \textcolor{blue}{approach} to give insight into the drivers of scavenging across vertebrates through time.
In common with any other forager be they grazer, browser or predator, scavengers past and present have had to balance their energetic costs with the gains of food. 
The main factors we considered namely, encounter rate, handling time and prey availability can be used to create a scale of scavenging whereupon any species can be placed in order \textcolor{blue}{to predict the qualitative importance} of carrion in it diet.
We hope this approach will be useful in the effort to explore this most understudied of feeding ecologies.

@@

\section*{Acknowledgments}
Thanks to Natalie Cooper for highlighting the potential for this review, and to Ara Monadjem and Deirdre McClean for their comments on the manuscript. We also thank Marcos Moleón and two other anonymous reviewers for very perceptive and helpful feedback on a previous version.
